---
title: "Plots"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```


```{r libraries}
library(tidyverse)
library(ggplot2)
```


```{r}
prsn_data_full <- read_csv("data/dataset121321WIDE.csv")

prsn_data <- prsn_data_full %>% select("id", "prolific_id", "c_time_in_nature_daysweek", "c_time_in_nature_hoursdaynew", "c_total_time_naturenew", "numparks_nq", "parkarea_nq", "proppark_nq", "popdensity_nq", "parkareaperperson_nq", "c_surroundings", "y1", "y2", "totalstress1cat","totalstress2cat", "changestress2", "catconscientiousness", "catemotional", "catagreeableness", "catopenness", "catextraversion")

```


```{r new variables}

# creating variable for personality type that combines low and high variables to one for plotting

newvar_prsn_data <- prsn_data %>% 
  mutate(
    # personality 
    conscientiousness = case_when(
      catconscientiousness == 3 ~ "3 - High",
      catconscientiousness == 2 ~ "2 - Medium",
      catconscientiousness == 1 ~ "1 - Low"
    ),
    emotional = case_when(
      catemotional == 3 ~ "3 - High",
      catemotional == 2 ~ "2 - Medium",
      catemotional == 1 ~ "1 - Low"
    ),
    agreeableness = case_when(
      catagreeableness == 3 ~ "3 - High",
      catagreeableness == 2 ~ "2 - Medium",
      catagreeableness == 1 ~ "1 - Low"
    ),
    openness = case_when(
      catopenness == 3 ~ "3 - High",
      catopenness == 2 ~ "2 - Medium",
      catopenness == 1 ~ "1 - Low"
    ),
    extraversion = case_when(
      catextraversion == 3 ~ "3 - High",
      catextraversion == 2 ~ "2 - Medium",
      catextraversion == 1 ~ "1 - Low"
    ),
    
    # park info
    numparks_nq = as.character(numparks_nq),
    parkarea_nq = as.character(parkarea_nq),
    proppark_nq = as.character(proppark_nq),
    popdensity_nq = as.character(popdensity_nq),
    parkareaperperson_nq = as.character(parkareaperperson_nq),
    c_surroundings = case_when(
      c_surroundings == "Other:" ~ "Other",
      TRUE ~ c_surroundings
    ),
    
    # direct nature
    days = c_time_in_nature_daysweek,
    hours = c_time_in_nature_hoursdaynew,
    total = c_total_time_naturenew,
    
    # stress
    
    stress1 = y1,
    stress2 = y2
    # "totalstress1cat","totalstress2cat", "changestress2"

  )

```


```{r find y bounds for nature and stress}
# Nature

natureDays_Qs <- quantile(newvar_prsn_data$days, na.rm = T)
natureDay_ylim <- c(0, 7)  

natureHours_Qs <- quantile(newvar_prsn_data$hours, na.rm = T)
natureHour_ylim <- c(0, (natureHours_Qs[4]+1.5*(natureHours_Qs[4] - natureHours_Qs[2]))*1.05) 

natureTotal_Qs <- quantile(newvar_prsn_data$total, na.rm = T)
natureTotal_ylim <- c(0, (natureTotal_Qs[4]+1.5*(natureTotal_Qs[4] - natureTotal_Qs[2]))*1.05) 



# stress
changestress_Qs <-quantile(newvar_prsn_data$changestress2, na.rm = T)
changestress_ylim <-  c( (changestress_Qs[2]*2), (changestress_Qs[4]+1.5*(changestress_Qs[4] - changestress_Qs[2]))*1.05) 

stress_ylim <- c(0, 40)

stresscat_ylim <- c(0, 5)

```


```{r 3 nature variables quartiles}

newvar_prsn_data <- newvar_prsn_data %>%
  mutate(
    natureDays_Q = case_when(
      days > natureDays_Qs[4] ~ "4",
      days > natureDays_Qs[3] ~ "3",
      days > natureDays_Qs[2] ~ "2",
      days >= natureDays_Qs[1] ~ "1"
    ),
    natureHours_Q = case_when(
      hours > natureHours_Qs[4] ~ "4",
      hours > natureHours_Qs[3] ~ "3",
      hours > natureHours_Qs[2] ~ "2",
      hours >= natureHours_Qs[1] ~ "1"
    ),
    natureTotal_Q = case_when(
      total > natureTotal_Qs[4] ~ "4",
      total > natureTotal_Qs[3] ~ "3",
      total > natureTotal_Qs[2] ~ "2",
      total >= natureTotal_Qs[1] ~ "1"
    )
  )

```


## Do personality features -how much time you're spending in nature? 

```{r conscientiousness and nature}

consc_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Conscientiousness",
  )+
  ylim(natureDay_ylim)
consc_natureDays


consc_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Conscientiousness",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Conscientiousness",
  )+
  ylim(natureHour_ylim)
consc_natureHours


consc_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Conscientiousness",
  )+
  ylim(natureTotal_ylim)
consc_natureTotal
```


```{r emotional and nature}

emo_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Emotionalness",
  )+
  ylim(natureDay_ylim)
emo_natureDays


emo_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Emotionalness",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Emotionalness",
  )+
  ylim(natureHour_ylim)
emo_natureHours


emo_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotional",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Emotional",
  )+
  ylim(natureTotal_ylim)
emo_natureTotal
```


```{r agreeableness and nature}

agree_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Agreeableness",
  )+
  ylim(natureDay_ylim)
agree_natureDays


agree_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Agreeableness",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Agreeableness",
  )+
  ylim(natureHour_ylim)
agree_natureHours


agree_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'total')) + 
  geom_boxplot() +
  labs(
    x = "Agreeableness",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Agreeableness",
  )+
  ylim(natureTotal_ylim)
agree_natureTotal
```


```{r openness and nature}

open_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Openness",
  )+
  ylim(natureDay_ylim)
open_natureDays


open_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Openness",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Openness",
  )+
  ylim(natureHour_ylim)
open_natureHours


open_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Openness",
  )+
  ylim(natureTotal_ylim)
open_natureTotal
```


```{r extraversion and nature}

extra_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Extraversion",
  )+
  ylim(natureDay_ylim)
extra_natureDays


extra_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Extraversion",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Extraversion",
  )+
  ylim(natureHour_ylim)
extra_natureHours


extra_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Extraversion",
  )+
  ylim(natureTotal_ylim)
extra_natureTotal
```


## Do neighborhood park features influence how much time you're spending in nature?

```{r num parks and nature}

np_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = "numparks_nq", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Number of Parks",
  )+
  ylim(natureDay_ylim)
np_natureDays


np_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = "numparks_nq", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Number of Parks in Tract",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Number of Parks",
  )+
  ylim(natureHour_ylim)
np_natureHours


np_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = "numparks_nq", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Number of Parks",
  )+
  ylim(natureTotal_ylim)
np_natureTotal
```


```{r park area and nature}

pa_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = "parkarea_nq", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Park Area in Tract",
  )+
  ylim(natureDay_ylim)
pa_natureDays


pa_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = "parkarea_nq", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Park Area in Tract",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Park Area in Tract",
  )+
  ylim(natureHour_ylim)
pa_natureHours


pa_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = "parkarea_nq", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Park Area in Tract",
  )+
  ylim(natureTotal_ylim)
pa_natureTotal
```


```{r prop parks and nature}

pp_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = "proppark_nq", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Proportion of Park Area in Tract",
  )+
  ylim(natureDay_ylim)
pp_natureDays


pp_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = "proppark_nq", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Proportion of Park Area in Tract",
  )+
  ylim(natureHour_ylim)
pp_natureHours


pp_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = "proppark_nq", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Proportion of Park Area in Tract",
  )+
  ylim(natureTotal_ylim)
pp_natureTotal
```


```{r pop density and nature}

pd_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = "popdensity_nq", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Population Density",
  )+
  ylim(natureDay_ylim)
pd_natureDays


pd_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = "popdensity_nq", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Population Density of Tract",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Population Density",
  )+
  ylim(natureHour_ylim)
pd_natureHours


pd_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = "popdensity_nq", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Population Density",
  )+
  ylim(natureTotal_ylim)
pd_natureTotal
```


```{r park burden and nature}

pb_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = "parkareaperperson_nq", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Park Burden",
  )+
  ylim(natureDay_ylim)
pb_natureDays


pb_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = "parkareaperperson_nq", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Park Burden of Tract",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Park Burden",
  )+
  ylim(natureHour_ylim)
pb_natureHours


pb_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = "parkareaperperson_nq", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Park Burden",
  )+
  ylim(natureTotal_ylim)
pb_natureTotal
```


```{r surroundings and nature}

sr_natureDays <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = "c_surroundings", y = 'days')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Number of Days with Time Spent in Nature",
    title = "Days in Nature by Surroundings",
  )+
  ylim(natureDay_ylim)
sr_natureDays


sr_natureHours <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = "c_surroundings", y = 'hours')) + 
  geom_boxplot() +
  labs(
    x = "Surroundings",
    y = "Hours in a Day Spent in Nature",
    title = "Hours in a Day in Nature by Surroundings",
  )+
  ylim(natureHour_ylim)
sr_natureHours


sr_natureTotal <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = "c_surroundings", y = 'total')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Total Minutes in a Week Spent in Nature",
    title = "Total Minutes in a Week in Nature by Surroundings",
  )+
  ylim(natureTotal_ylim)
sr_natureTotal
```


## Does personality type category influence total level of stress?

```{r personality and stress1}

consc_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Conscientiousness",
  )+
  ylim(stress_ylim)


emo_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Emotionalness",
  )+
  ylim(stress_ylim)



agree_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Agreeableness",
  )+
  ylim(stress_ylim)



open_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Openness",
  )+
  ylim(stress_ylim)



extra_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Extraversion",
  )+
  ylim(stress_ylim)



```


```{r personality and stress2}

consc_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Conscientiousness",
  )+
  ylim(stress_ylim)


emo_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Emotionalness",
  )+
  ylim(stress_ylim)



agree_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Agreeableness",
  )+
  ylim(stress_ylim)



open_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Openness",
  )+
  ylim(stress_ylim)



extra_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Extraversion",
  )+
  ylim(stress_ylim)


```


```{r personality and totalstress1cat}

consc_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Conscientiousness",
  )+
  ylim(stresscat_ylim)


emo_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Emotionalness",
  )+
  ylim(stresscat_ylim)



agree_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Agreeableness",
  )+
  ylim(stresscat_ylim)



open_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Openness",
  )+
  ylim(stresscat_ylim)



extra_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Extraversion",
  )+
  ylim(stresscat_ylim)


```


```{r personality and totalstress2cat}

consc_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Conscientiousness",
  )+
  ylim(stresscat_ylim)


emo_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Emotionalness",
  )+
  ylim(stresscat_ylim)



agree_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Agreeableness",
  )+
  ylim(stresscat_ylim)



open_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Openness",
  )+
  ylim(stresscat_ylim)



extra_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Extraversion",
  )+
  ylim(stresscat_ylim)


```


```{r personality and changestress2}

consc_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(conscientiousness)) %>%
  ggplot(
         aes_string( x = 'conscientiousness', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Conscientiousness",
    y = "Change in Stress",
    title = "Change in Stress by Conscientiousness",
  )+
  ylim(changestress_ylim)


emo_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(emotional)) %>%
  ggplot(
         aes_string( x = 'emotional', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Emotionalness",
    y = "Change in Stress",
    title = "Change in Stress by Emotionalness",
  )+
  ylim(changestress_ylim)



agree_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(agreeableness)) %>%
  ggplot(
         aes_string( x = 'agreeableness', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Agreeableness",
    y = "Change in Stress",
    title = "Change in Stress by Agreeableness",
  )+
  ylim(changestress_ylim)



open_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(openness)) %>%
  ggplot(
         aes_string( x = 'openness', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Openness",
    y = "Change in Stress",
    title = "Change in Stress by Openness",
  )+
  ylim(changestress_ylim)



extra_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(extraversion)) %>%
  ggplot(
         aes_string( x = 'extraversion', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Extraversion",
    y = "Change in Stress",
    title = "Change in Stress by Extraversion",
  )+
  ylim(changestress_ylim)


```


```{r personality and stress plots}

consc_stress1
consc_stress2
consc_totalstress1cat
consc_totalstress2cat
consc_changestress2

emo_stress1
emo_stress2
emo_totalstress1cat
emo_totalstress2cat
emo_changestress2

agree_stress1
agree_stress2
agree_totalstress1cat
agree_totalstress2cat
agree_changestress2

open_stress1
open_stress2
open_totalstress1cat
open_totalstress2cat
open_changestress2

extra_stress1
extra_stress2
extra_totalstress1cat
extra_totalstress2cat
extra_changestress2

```


## Do park features influence the level of stress?

```{r numparks and stress}

np_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = 'numparks_nq', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Number of Parks in Tract",
  )+
  ylim(stress_ylim)
np_stress1


np_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = 'numparks_nq', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Number of Parks in Tract",
  )+
  ylim(stress_ylim)
np_stress2


np_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = 'numparks_nq', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Number of Parks in Tract",
  )+
  ylim(stresscat_ylim)
np_totalstress1cat


np_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = 'numparks_nq', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Number of Parks in Tract",
  )+
  ylim(stresscat_ylim)
np_totalstress2cat


np_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(numparks_nq)) %>%
  ggplot(
         aes_string( x = 'numparks_nq', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Number of Parks in Tract",
    y = "Change in Stress",
    title = "Change in Stress by Number of Parks in Tract",
  )+
  ylim(changestress_ylim)
np_changestress2

```


```{r parkarea and stress}

pa_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = 'parkarea_nq', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Park Area in Tract",
  )+
  ylim(stress_ylim)
pa_stress1


pa_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = 'parkarea_nq', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Park Area in Tract",
  )+
  ylim(stress_ylim)
pa_stress2


pa_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = 'parkarea_nq', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Park Area in Tract",
  )+
  ylim(stresscat_ylim)
pa_totalstress1cat


pa_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = 'parkarea_nq', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Park Area in Tract",
  )+
  ylim(stresscat_ylim)
pa_totalstress2cat


pa_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(parkarea_nq)) %>%
  ggplot(
         aes_string( x = 'parkarea_nq', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Area in Tract",
    y = "Change in Stress",
    title = "Change in Stress by Park Area in Tract",
  )+
  ylim(changestress_ylim)
pa_changestress2

```


```{r proppark and stress}

pp_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = 'proppark_nq', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Proportion of Park Area in Tract",
  )+
  ylim(stress_ylim)
pp_stress1


pp_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = 'proppark_nq', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Proportion of Park Area in Tract",
  )+
  ylim(stress_ylim)
pp_stress2


pp_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = 'proppark_nq', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Proportion of Park Area in Tract",
  )+
  ylim(stresscat_ylim)
pp_totalstress1cat


pp_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = 'proppark_nq', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Proportion of Park Area in Tract",
  )+
  ylim(stresscat_ylim)
pp_totalstress2cat


pp_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(proppark_nq)) %>%
  ggplot(
         aes_string( x = 'proppark_nq', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Proportion of Park Area in Tract",
    y = "Change in Stress",
    title = "Change in Stress by Proportion of Park Area in Tract",
  )+
  ylim(changestress_ylim)
pp_changestress2

```


```{r popdensity and stress}

pd_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = 'popdensity_nq', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Population Density",
  )+
  ylim(stress_ylim)
pd_stress1


pd_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = 'popdensity_nq', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Population Density",
  )+
  ylim(stress_ylim)
pd_stress2


pd_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = 'popdensity_nq', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Population Density",
  )+
  ylim(stresscat_ylim)
pd_totalstress1cat


pd_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = 'popdensity_nq', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Population Density",
  )+
  ylim(stresscat_ylim)
pd_totalstress2cat


pd_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(popdensity_nq)) %>%
  ggplot(
         aes_string( x = 'popdensity_nq', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Population Density of Tract",
    y = "Change in Stress",
    title = "Change in Stress by Population Density",
  )+
  ylim(changestress_ylim)
pd_changestress2

```


```{r park burden and stress}

pd_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = 'parkareaperperson_nq', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Park Burden",
  )+
  ylim(stress_ylim)
pd_stress1


pd_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = 'parkareaperperson_nq', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Park Burden",
  )+
  ylim(stress_ylim)
pd_stress2


pd_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = 'parkareaperperson_nq', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Park Burden",
  )+
  ylim(stresscat_ylim)
pd_totalstress1cat


pd_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = 'parkareaperperson_nq', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Park Burden",
  )+
  ylim(stresscat_ylim)
pd_totalstress2cat


pd_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(parkareaperperson_nq)) %>%
  ggplot(
         aes_string( x = 'parkareaperperson_nq', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Park Burden of Tract",
    y = "Change in Stress",
    title = "Change in Stress by Park Burden",
  )+
  ylim(changestress_ylim)
pd_changestress2

```


```{r surroundings and stress}

pd_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = 'c_surroundings', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Surroundings",
  )+
  ylim(stress_ylim)
pd_stress1


pd_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = 'c_surroundings', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Surroundings",
  )+
  ylim(stress_ylim)
pd_stress2


pd_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = 'c_surroundings', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Surroundings",
  )+
  ylim(stresscat_ylim)
pd_totalstress1cat


pd_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = 'c_surroundings', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Surroundings",
  )+
  ylim(stresscat_ylim)
pd_totalstress2cat


pd_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(c_surroundings)) %>%
  ggplot(
         aes_string( x = 'c_surroundings', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Surroundings",
    y = "Change in Stress",
    title = "Change in Stress by Surroundings",
  )+
  ylim(changestress_ylim)
pd_changestress2

```


## Does how much time you're spending influence (number days, new number of hours, and total dosage) influence total stress?

```{r nature days and stress}

days_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(natureDays_Q)) %>%
  ggplot(
         aes_string( x = 'natureDays_Q', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Days with Time Spent in Nature",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Quartile of Days with Time Spent in Nature",
  )+
  ylim(stress_ylim)
days_stress1


days_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureDays_Q)) %>%
  ggplot(
         aes_string( x = 'natureDays_Q', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Days with Time Spent in Nature",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Quartile of Days with Time Spent in Nature",
  )+
  ylim(stress_ylim)
days_stress2


days_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureDays_Q)) %>%
  ggplot(
         aes_string( x = 'natureDays_Q', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Days with Time Spent in Nature",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Quartile of Days with Time Spent in Nature",
  )+
  ylim(stresscat_ylim)
days_totalstress1cat


days_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureDays_Q)) %>%
  ggplot(
         aes_string( x = 'natureDays_Q', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Days with Time Spent in Nature",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Quartile of Days with Time Spent in Nature",
  )+
  ylim(stresscat_ylim)
days_totalstress2cat


days_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureDays_Q)) %>%
  ggplot(
         aes_string( x = 'natureDays_Q', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Days with Time Spent in Nature",
    y = "Change in Stress",
    title = "Change in Stress by Quartile of Days with Time Spent in Nature",
  )+
  ylim(changestress_ylim)
days_changestress2

```


```{r nature hours and stress}

hours_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(natureHours_Q)) %>%
  ggplot(
         aes_string( x = 'natureHours_Q', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours in Nature",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Quartile of Hours in Nature",
  )+
  ylim(stress_ylim)
hours_stress1


hours_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureHours_Q)) %>%
  ggplot(
         aes_string( x = 'natureHours_Q', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours in Nature",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Quartile of Hours in Nature",
  )+
  ylim(stress_ylim)
hours_stress2


hours_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureHours_Q)) %>%
  ggplot(
         aes_string( x = 'natureHours_Q', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours in Nature",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Quartile of Hours in Nature",
  )+
  ylim(stresscat_ylim)
hours_totalstress1cat


hours_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureHours_Q)) %>%
  ggplot(
         aes_string( x = 'natureHours_Q', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours in Nature",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Quartile of Hours in Nature",
  )+
  ylim(stresscat_ylim)
hours_totalstress2cat


hours_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureHours_Q)) %>%
  ggplot(
         aes_string( x = 'natureHours_Q', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours in Nature",
    y = "Change in Stress",
    title = "Change in Stress by Quartile of Hours in Nature",
  )+
  ylim(changestress_ylim)
hours_changestress2

```


```{r nature total and stress}

hours_stress1 <-
  newvar_prsn_data %>%
  filter(!is.na(natureTotal_Q)) %>%
  ggplot(
         aes_string( x = 'natureTotal_Q', y = 'stress1')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Total Time Spent in Nature",
    y = "Total Stress at S1",
    title = "Total Stress at S1 by Quartile of Total Time Spent in Nature",
  )+
  ylim(stress_ylim)
hours_stress1


hours_stress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureTotal_Q)) %>%
  ggplot(
         aes_string( x = 'natureTotal_Q', y = 'stress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Total Time Spent in Nature",
    y = "Total Stress at S2",
    title = "Total Stress at S2 by Quartile of Total Time Spent in Nature",
  )+
  ylim(stress_ylim)
hours_stress2


hours_totalstress1cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureTotal_Q)) %>%
  ggplot(
         aes_string( x = 'natureTotal_Q', y = 'totalstress1cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Total Time Spent in Nature",
    y = "Categorized Stress at S1",
    title = "Categorized Stress at S1 by Quartile of Total Time Spent in Nature",
  )+
  ylim(stresscat_ylim)
hours_totalstress1cat


hours_totalstress2cat <-
  newvar_prsn_data %>%
  filter(!is.na(natureTotal_Q)) %>%
  ggplot(
         aes_string( x = 'natureTotal_Q', y = 'totalstress2cat')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Total Time Spent in Nature",
    y = "Categorized Stress at S2",
    title = "Categorized Stress at S2 by Quartile of Total Time Spent in Nature",
  )+
  ylim(stresscat_ylim)
hours_totalstress2cat


hours_changestress2 <-
  newvar_prsn_data %>%
  filter(!is.na(natureTotal_Q)) %>%
  ggplot(
         aes_string( x = 'natureTotal_Q', y = 'changestress2')) + 
  geom_boxplot(outlier.shape = NA) +
  labs(
    x = "Quartile of Hours with in Nature",
    y = "Change in Stress",
    title = "Change in Stress by Quartile of Total Time Spent in Nature",
  )+
  ylim(changestress_ylim)
hours_changestress2

```




